
\section*{Extra Credit 3: Adversarial Alien Obfuscation}

\subsection*{Methodology}
To test the robustness of the language model against varying degrees of linguistic obfuscation, we replaced the original alien operator names (\texttt{flarn}, \texttt{glorp}, etc.) with four alternative mapping schemes:
\begin{itemize}
    \item \textbf{Semantic}: Real English words that loosely hint at the mathematical operation (e.g., \texttt{combine} for addition, \texttt{shrink} for subtraction).
    \item \textbf{Misleading}: Real English words that suggest completely unrelated or incorrect concepts (e.g., \texttt{paint}, \texttt{dance}).
    \item \textbf{Gibberish}: Random, non-semantic character strings (e.g., \texttt{qahft}, \texttt{bsdmr}).
    \item \textbf{Unicode}: Non-ASCII mathematical or arbitrary symbols (e.g., $\Delta$, $\oplus$).
\end{itemize}
These prompts were evaluated zero-shot with system instructions defining the behavior of the newly mapped operators.

\subsection*{Quantitative Results}
The evaluation results across the different obfuscation strategies are detailed in Table \ref{tab:obfuscation_results}.

\begin{table}[h]
\centering
\begin{tabular}{l c c c c}
\toprule
\textbf{Scheme} & \textbf{Overall Acc.} & \textbf{Level 1 Acc.} & \textbf{Level 2 Acc.} & \textbf{Level 3 Acc.} \\
\midrule
Original & 11.3\% & 30.0\% & 2.0\% & 2.0\% \\
Gibberish & 10.0\% & 28.0\% & 0.0\% & 2.0\% \\
Unicode & 6.0\% & 16.0\% & 0.0\% & 2.0\% \\
Semantic & 0.0\% & 0.0\% & 0.0\% & 0.0\% \\
Misleading & 0.0\% & 0.0\% & 0.0\% & 0.0\% \\
\bottomrule
\end{tabular}
\caption{Accuracy of the Qwen-0.5B-Instruct model under various obfuscation schemes.}
\label{tab:obfuscation_results}
\end{table}

\subsection*{Analysis and Discussion}

The results reveal an unexpected failure mode: both the \textbf{Semantic} and \textbf{Misleading} schemes resulted in a catastrophic 0.0\% accuracy. This complete failure was not necessarily due to an inability to perform the underlying mathematics, but rather a \textbf{formatting collapse} triggered by the semantic weight of the prompt.

When presented with purely logical or meaningless symbols (Original, Gibberish, and Unicode), the model treated the prompt as an abstract puzzle and strictly adhered to the required output format (\texttt{Final Answer: <number>}). However, when real English words (\texttt{combine}, \texttt{paint}) were introduced into the mathematical expressions, it triggered the model's pre-trained conversational priors. The model abandoned the strict formatting constraint, outputting conversational sentences such as \texttt{The final answer is 23.} or \texttt{The final answer is 1.3.} Because the extraction script required a strict regex match, these conversational deviations resulted in widespread extraction failures.

This demonstrates that semantic and misleading obfuscation can actively degrade model performance by breaking the formal structure of the prompt, overriding the system instructions with pre-trained conversational habits.


